---
title: "NBATools package demo"
author: "Chongxi Wang"
date: "May 25, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Package

You should install "NBATools" first. You can find the instruction in "README.md".

```{r}
library(NBATools)
```

## Demo1: Salary Prediction

```{r}
print(salaryPred("LeBron James"))
```

```{r}
print(salaryPred("Stephen Curry"))
```

## Demo2: Game Result Prediction

Prepare data.

```{r}
CLE = subset(player_salary, Tm=="CLE", Player)[,1]
GSW = subset(player_salary, Tm=="GSW", Player)[,1]
```

Predict CLE vs GSW, CLE loses.

```{r}
print(gamePred(CLE, GSW))
```

## Demo3: Team Quality Prediction

Prepare data.

```{r}
CLE = subset(player_salary, Tm=="CLE", Player)[,1]
BOS = subset(player_salary, Tm=="BOS", Player)[,1]
```

Predict the quality of CLE with accuracy = 1000.

```{r}
print(teamQualityPred(CLE, accuracy=1000))
```

Predict the quality of BOS with accuracy = 500.

```{r}
print(teamQualityPred(BOS, accuracy=500))
```

## Demo4: Free-Agent Signing Proposal

Prepare data.

```{r}
CLE = subset(player_salary, Tm=="CLE", Player)[,1]
BOS = subset(player_salary, Tm=="BOS", Player)[,1]
```

Provide signing proposal of CLE with salary cap = 130000000 and accuracy = 10.

```{r}
freeAgentProp(CLE, cap=130000000, accuracy=10)
```

Provide signing proposal of BOS with salary cap = 121000000 and accuracy = 20.

```{r}
freeAgentProp(BOS, cap=121000000, accuracy=20)
```

## Demo5: Trade Proposal

Prepare data.

```{r}
CLE_before <- c("LeBron James", "Kevin Love", "Tristan Thompson", "J.R. Smith", "Kyle Korver", "Cedi Osman", "Jose Calderon", "Jeff Green", "Ante Zizic", "Isaiah Thomas", "Dwyane Wade", "Derrick Rose", "Channing Frye", "Iman Shumpert", "Jae Crowder")
CLE_after <- subset(player_salary, Tm=="CLE", Player)[,1]
print("Player list before trade:")
print(CLE_before)
print("Player list after trade:")
print(CLE_after)
```

Provide trade proposal of a certain trade.

```{r}
tradeProp(CLE_before, CLE_after, accuracy=1000)
```
